%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{About Myself}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}
  I'm Josh. I’m a software developer with around 11 years of commercial experience. I live in the Blue Mountains west of Sydney, so I'm mainly interested in remote opportunities.

  My expertise is in functional programming, service-oriented cloud architectures, large-scale data processing pipelines, and web development. I'm also passionate about the environment, privacy, civil liberties, and education.

  I spent most of 2020 working on my own startup in the digital identity space. However, due to some significant life events (namely my adorable daughter, Madeline) I'm putting that on the back-burner for the forseeable future.

  For my next role I'm looking for something where I can step up and take on more responsibility. In particular, a role where I can work across both software development and product management would be ideal.

  I graduated from the Australian National University in 2014 with a Bachelor of Computer
  Science (Honours) - one of their most challenging and selective degrees.

  At university I focused on large scale parallel and distributed systems; various machine learning, data mining and AI techniques; and a healthy dose of pure theory and mathematics.

\end{cvletter}